### 2016-06-17 paper/evaluation.tex
responded to some feedback
added in proof outline

\section{Evaluation}
We ran our algorithm on tests validating our ability to handle regular
expression equivalences, tests derived from the Augeus test suite, and from
tests derived from the FlashFill tests.

\input{fig_runtimes-table}
\subsection{Speed}
Figure~\ref{fig:runtimes-table} provides the runtime of our algorithm on our
test suite.
In this figure, we want to minimize runtime, as a smaller runtime means we were
able to synthesize very efficiently.
We found that, on many of our difficult examples, our algorithm was able to find
the appropriate lens very quickly.

@@

\input{fig_examples-required-table}
As we see in Figure~\ref{fig:examples-required-table}, examples are not too
important for synthesizing bijective lenses.\bcp{If that's really the
  conclusion, then maybe we should have written a paper about synthesizing
  bijective lenses {\em without} examples!  But I don't think we can
  actually conclude this from the examples we have.  }
Because bijective lenses have very few well typed programs, compared to the
number of functions, oftentimes just a few examples is sufficient.
As would be expected, the functions that have to make choices about the
locations of where data goes are those that require more examples.
In particular, the address problem requires more examples, because it must make
choices of where information goes, like which name is the a person's first name,
and which is their last.

\input{fig_expanded-time-table}
\subsection{Importance of User Defined Data Types}

>>>>

\section{Evaluation}
We ran our algorithm on tests validating our ability to handle regular
expression equivalences, tests derived from the Augeus test suite, and from
tests derived from the FlashFill tests.
The values presented are the arithmetic means of 10 test runs.
The tests were run on a 2.5 GHz Intel Core i7 processor, with
16 GB of 1600 MHz DDR3, running Mac OS X Yosemite.

% fig:runtimes-table
\begin{figure}
\centering
%\begin{tabular}{|l|c|}

\csvreader[tabular=|l|l|,
    table head=\hline\textbf{Test} & \textbf{Time (s)} \\\hline,
    late after line = \\\hline]
{generated-data/data.csv}{Test=\Test,ComputationTime=\ComputationTime}
{\Test{} & \ComputationTime{}}

%\hline\textbf{Test} & \textbf{Examples Required}
%\\\hline\hline
%\csvreader[head to column names]{generated-data/data.csv}{}
%{\Test& \ExamplesRequired\\\hline}
%\end{tabular}
\caption{Runtime Table\bcp{Hard to read, with all the zeros.  Maybe better
    to display as a (log-scale) graph?  More seriously, we'll need to
    explain the examples someplace, say why we chose them, maybe group them
    in some way, ...  Why ws this the right set of tests?}}
\label{fig:runtimes-table}
\end{figure}

\subsection{Speed}
Figure~\ref{fig:runtimes-table} provides the runtime of our algorithm on our
test suite.
In this figure, we want to minimize runtime, as a smaller runtime means we were
able to synthesize very efficiently.
We found that, on many of our difficult examples, our algorithm was able to find
the appropriate lens very quickly.

@@

% fig:examples-required-table
\begin{figure}
\centering
%\begin{tabular}{|l|c|}

\csvreader[tabular=|l|l|,
    table head=\hline\textbf{Test} & \textbf{Example Count} \\\hline,
    late after line = \\\hline]%
{generated-data/data.csv}{Test=\Test,ExamplesRequired=\ExamplesRequired}%
{\Test{} & \ExamplesRequired{}}%

%\hline\textbf{Test} & \textbf{Examples Required}
%\\\hline\hline
%\csvreader[head to column names]{generated-data/data.csv}{}
%{\Test& \ExamplesRequired\\\hline}
%\end{tabular}
\caption{Examples Required Table\bcp{Is this table showing us that the
    examples we chose are mostly not very interesting?}}
\label{fig:examples-required-table}
\end{figure}

As we see in Figure~\ref{fig:examples-required-table}, examples are not too
important for synthesizing bijective lenses.\bcp{If that's really the
  conclusion, then maybe we should have written a paper about synthesizing
  bijective lenses {\em without} examples!  But I don't think we can
  actually conclude this from the examples we have.  }
Because bijective lenses have very few well typed programs, compared to the
number of functions, oftentimes just a few examples is sufficient.
As would be expected, the functions that have to make choices about the
locations of where data goes are those that require more examples.
In particular, the address problem requires more examples, because it must make
choices of where information goes, like which name is the a person's first name,
and which is their last.

% fig:expanded-time-table
\begin{figure}
\centering
%\begin{tabular}{|l|c|}

\csvreader[tabular=|l|l|,
    table head=\hline\textbf{Test} & \textbf{Time (s)} \\\hline,
    late after line = \\\hline]%
{generated-data/data.csv}{Test=\Test,ForceExpandTime=\ForceExpandTime}%
{\Test{} & \ForceExpandTime{}}%

%\hline\textbf{Test} & \textbf{Examples Required}
%\\\hline\hline
%\csvreader[head to column names]{generated-data/data.csv}{}
%{\Test& \ExamplesRequired\\\hline}
%\end{tabular}
\caption{Expanded Regexp Runtime Table}
\label{fig:expanded-time-table}
\end{figure}
\subsection{Importance of User Defined Data Types}
